DOpElib: Differential Equations and Optimization Environment; A Goal Oriented Software Library for Solving PDEs and Optimization Problems

### 2012-11-21 Paper_May_2012/main_tw.tex
main TW: Weitere Anmerkungen hinzugefuegt

\end{lstlisting}
Finally, the program is started by
\begin{lstlisting}

@@

\newpage
\subsection{Compliance minimization}
In this example, we consider the compliance minimization of a standard MBB-Beam. 
The thickness variable is allowed to take intermediate value apart from $0$ and $1$,
i.e., we consider a variable thickness sheet. The discretization is done 
using $Q_2$ elements for the displacement and discontinuous $P_0$ elements for the 
thickness.
\begin{figure}
\centering
\includegraphics[width=1.\textwidth, viewport=150 0 1024 500, clip]{Pictures/MBB.png}
\caption{Thickness distribution for the MBB-beam minimum compliance problem.} 
\label{res:mbb}
\end{figure}
A typical thickness distribution is shown in Figure~\ref{res:mbb}.

>>>>

\end{lstlisting}
\todo{Finde diesen Schlusssatz komisch}
Finally, the program is started by
\begin{lstlisting}

@@

\newpage
\subsection{Compliance minimization}
\todo{Was ist MBB? Konnest Du vielleicht auch eine Referenz zur Konfiguration angeben?}
In this example, we consider the compliance minimization of a standard MBB-Beam. 
The thickness variable is allowed to take intermediate value apart from $0$ and $1$,
i.e., we consider a variable thickness sheet. The discretization is done 
using $Q_2$ elements for the displacement and discontinuous $P_0$ elements for the 
thickness.
\begin{figure}
\centering
\includegraphics[width=1.\textwidth, viewport=150 0 1024 500, clip]{Pictures/MBB.png}
\caption{Thickness distribution for the MBB-beam minimum compliance problem.} 
\label{res:mbb}
\end{figure}
A typical thickness distribution is shown in Figure~\ref{res:mbb}.
